Handbook streamFind: Backend

### 2025-09-03 README.Rmd
updated with app fix

Start the Docker container:
`docker run -it -p 3838:3838 -p 8787:8787 -v $(pwd):/app my-r-app`

>>>>

Start the Docker container:

**For Linux/macOS/bash:**
```bash
docker run -it -p 3838:3838 -p 8787:8787 -v $(pwd):/app my-r-app
```

**For Windows PowerShell:**
```powershell
docker run -it -p 3838:3838 -p 8787:8787 -v "${PWD}:/app" my-r-app
```
